Meet the team

### 2025-08-26 index.qmd
add lab manual link

@@

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Calalo J, Ngo TT, Buggeln JH, Roth AR, Peters CS, Kurtzer IL, Carter MJ, & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}

>>>>

<font color="#d08770">[August 26 2025].</font> **New member**. Welcome to Michael Croteau, who is starting his M.Sc studies. Michael previously completed his undergraduate project and thesis courses in the lab.

@@

### 2025-08-26 news.qmd
add new paper acceptance
add doi for jneurosci paper
add lab manual link

>>>>

<font color="#d08770">[August 26 2025].</font> **New member**. Welcome to Michael Croteau, who is starting his M.Sc studies. Michael previously completed his undergraduate project and thesis courses in the lab.

<font color="#d08770">[July 31 2025].</font> **New Preprint**. Sullivan SR, Buggeln JH, Calalo JA, Ngo TT, Semrau JA, Carter MJ, & Cashaback JGA. Involuntary feedback responses reflect a representation of partner actions. *bioR$\chi$iv*. [https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}

<font color="#d08770">[June 13 2024].</font> **Paper accepted**. Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}

### 2025-08-26 team.qmd
update team page
add lab manual link

<div class="team-member">
  <img src="images/mikayla-lalli.jpg" alt="images/mikayla-lalli.jpg" class="team-img">
  <div class="team-info">
  <h4> Mikayla Lalli, M.Sc. </h4>
  <p> Ph.D. Student </p>
  <p> lallim1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/nour-al-afif.jpg" alt="images/nour-al-afif.jpg" class="team-img">
  <div class="team-info">
  <h4> Nour Al Afif, M.Sc. </h4>
  <p> Ph.D. Student </p>
  <p> alafin1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
  <div class="team-info">
  <h4> Michael Croteau </h4>
  <p> Incoming M.Sc. Student - Fall 2025 </p>
  <p> croteaum [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/maria-alex.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Maria Alex </h4>
  <p> Undergraduate Research Assistant </p>
  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Kaylen Rathwell </h4>
  <p> Lab Technician </p>
  <p> motorlab [at] mcmaster [dot] ca </p>
  </div>
</div>

>>>>

<div class="team-member">
  <img src="images/mikayla-lalli.jpg" alt="images/mikayla-lalli.jpg" class="team-img">
  <div class="team-info">
  <h4> Mikayla Lalli, M.Sc. </h4>
  <p> Ph.D. Candidate </p>
  <p> lallim1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/nour-al-afif.jpg" alt="images/nour-al-afif.jpg" class="team-img">
  <div class="team-info">
  <h4> Nour Al Afif, M.Sc. </h4>
  <p> Ph.D. Candidate </p>
  <p> alafin1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
  <div class="team-info">
  <h4> Michael Croteau </h4>
  <p> M.Sc. Student </p>
  <p> croteaum [at] mcmaster [dot] ca </p>
  </div>
</div>
